(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Confirmation of $N$ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-05 ms.tex
not sure how to unrotate pages...

\paperit{} simultaneously fit both the systematics and potential planetary transit signals
in a search for transiting planets. 
The authors of that paper assume that the dominant trends in the observed stellar light
curves are caused by spacecraft motion and are shared among many stars. \anytodo{Among,
right? Not between?}
They then run PCA on all stars to measure the dominant modes, modeling each star as a 
linear combination of 150 of these ``eigen light curves'' and a transit signal.
This method enables fitting without over-fitting, and also permits marginalization over
uncertainties induced by the noise model.
Therefore, any uncertainties in the systematics can be propogated into uncertainties in
detected planet parameters, instead of assuming the systematics are understood perfectly.
Using this technique, \paperit{} detect 36 planet candidates orbiting 31 stars in \KT\
\Ci\ data.

@@

In this paper, we present stellar and planetary parameters for each system.
Given these parameters and the transit data, as well as archival imaging, ground-based
seeing limited survey data, and adaptive optics imaging, we are able to confirm 
\anytodo{Number} of these systems as transiting planets at the \anytodo{Sigma} confidence
level. We also are able to confirm \anytodo{Number} of these systems as false positives.

@@

Such a scheme enables us to infer the statistical uncertainties on the
mass, radius, and effective temperature.
However, we are subject to biases induced by systematics in the models themselves.
There is some evidence that the Dartmouth models may underpredict 
radii by $\sim 15\%$ when compared to other methods \citep{Newton15,
Montet15}. 
Such an effect may be the result of the Dartmouth model reliance on BT-Settl
atmospheres, which have been shown to predict near-IR colors that are too blue
\citep{Thompson14}.
We find that by measuring stellar parameters without any WISE data (that is, using
only $BVgriJHK$), we largely reproduce the same effective temperatures as when
the WISE data is included. 
However, at the low-mass end including the WISE data systematically increases the 
measured radius and increases \logg, as shown in \btmtodo{Figure}.
Suggestively, spectroscopic stellar parameters of EPIC 201912552 
(\textsection\ref{Spexobs}) suggest the derived photometric properties better 
represent the true physical parameters when the WISE data is included.

@@

This is Dan.

@@

\section{False Positive Analysis}
\subsection{Adaptive Optics Imaging}

@@

\subsection{Multiple Planet Systems}
Five of the systems identified by \paperit\ are candidates to be multiply-transiting
systems. 
One of these is EPIC 201367065, a three-planet system originally announced by
\citet{Crossfield15}. 
Another of these is EPIC 201505350 \citep{Armstrong15b}, a two-planet system with the
orbital periods of the two planets near a 3:2 period commensurability.
The remaining three are all representative of the multiple-planet systems observed by
\kep \citep{Lissauer11b, Fabrycky14}.
Two of the systems are near a period commensurability and all three consist of 
mini-Neptune sized planets.
Like in the \kep\ field, the false positive rate we measure for the multiple planet sample
here ($0/10$) is lower than for the single systems \citep{Lissauer12, Rowe14}.

@@

>>>>

\paperit{} simultaneously fit both the systematics and potential planetary transit signals
in a search for transiting planets.
The authors of that paper assume that the dominant trends in the observed stellar light
curves are caused by spacecraft motion and are shared among many stars. \anytodo{Among,
right? Not between?}
They then run PCA on all stars to measure the dominant modes, modeling each star as a

linear combination of 150 of these ``eigen light curves'' and a transit signal.
This method enables fitting without over-fitting, and also permits marginalization 
over
uncertainties induced by the noise model.
Therefore, any uncertainties in the systematics can be propogated into uncertainties 
in
detected planet parameters, instead of assuming the systematics are understood 
perfectly.
Using this technique, \paperit{} detect 36 planet candidates orbiting 31 stars in \KT\
\Ci\ data.

@@

In this paper, we present stellar and planetary parameters for each system.

Given these parameters and the transit data, as well as archival imaging, ground-based
seeing limited survey data, and adaptive optics imaging, we are able to confirm
\anytodo{Number} of these systems as transiting planets at the \anytodo{Sigma} confidence
level. We also are able to confirm \anytodo{Number} of these systems as false positives.

@@

Such a scheme enables us to infer the statistical uncertainties on the
mass, radius, and effective temperature.

However, we are subject to biases induced by systematics in the models themselves.
There is some evidence that the Dartmouth models may underpredict
radii by $\sim 15\%$ when compared to other methods \citep{Newton15,
Montet15}.
Such an effect may be the result of the Dartmouth model reliance on BT-Settl
atmospheres, which have been shown to predict near-IR colors that are too blue
\citep{Thompson14}.
We find that by measuring stellar parameters without any WISE data (that is, using
only $BVgriJHK$), we largely reproduce the same effective temperatures as when
the WISE data is included.
However, at the low-mass end including the WISE data systematically increases the
measured radius and increases \logg, as shown in \btmtodo{Figure}.
Suggestively, spectroscopic stellar parameters of EPIC 201912552
(\textsection\ref{Spexobs}) suggest the derived photometric properties better
represent the true physical parameters when the WISE data is included.

@@

This is Dan. 
[for logic flow, perhaps this section should follow the FP section?]

@@

\section{False Positive Analysis}

As has been well known from the early days of transit searches, it is 
possible for an eclipsing binary star to masquerade as a transiting 
planet if (a) it is a highly grazing eclipse, or (b) the binary system
comprises only a small fraction of the total light in the photometric
aperture, resulting in a diluted eclipse depth.
When possible, such astrophsycial false positive scenarios are traditionally
ruled out by detailed follow-up observations, such as high-resolution
imaging or radial-velocity measurements.  
However, the \kep\ mission, with its thousands of planet candidates
around mostly faint stars, necessitated a paradigm shift---a move 
toward probabilistic interpretation of transit signals, rather than 
comprehensive follow-up of each individual candidate.

\citet{Morton12} described an automated method to calculate the
probability that a planet candidate might be caused by an
astrophysical false positive.  
This method uses population simulations
of false positive scenarios and true transiting planets to quantify
the typical shape of each, and combines prior information about the
populations of field stars and multiple star systems in order to
determine the probability that the observed signal may be a false
positive.  
Similar in spirit to other published methods of probabilistic
validation, such as Blender \citep{} and PASTIS \citep{}, it
has the advantage of being computationally less demanding and 
fully automated, and thus easily applied in batch to a large number of
candidates.

\subsection{Adaptive Optics Imaging}

@@

\subsection{Multiple Planet Systems}
Five of the systems identified by \paperit\ are candidates to be multiply-transiting
systems.
One of these is EPIC 201367065, a three-planet system originally announced by

\citet{Crossfield15}.
Another of these is EPIC 201505350 \citep{Armstrong15b}, a two-planet system with the
orbital periods of the two planets near a 3:2 period commensurability.
The remaining three are all representative of the multiple-planet systems observed 
by
\kep \citep{Lissauer11b, Fabrycky14}.
Two of the systems are near a period commensurability and all three consist of
mini-Neptune sized planets.
Like in the \kep\ field, the false positive rate we measure for the multiple planet 
sample
here ($0/10$) is lower than for the single systems \citep{Lissauer12, Rowe14}.

@@

\include{table_planets}
